---
title: "World Happiness Report in 2017"
output: html_document
---



## Including Plots
## 0_Introduction
The pursuit of happiness had been a part of humanity longer than some may think; some even argue that it’s the reason we continue to do more than just exist. Evidence of this stems back to Ancient Greece, when Philosophers such as Aristotle wrote about it in many of his texts. In fact, the “pursuit of happiness” was a vital part of the United States Declaration of Independence, written in 1776. With Thomas Jefferson stating how he believed that happiness is attainable by gaining knowledge and living a self-sufficient life surrounded by friends. If we look at the multitude of global religions, we see a similar importance placed on the idea of happiness.
```{r}
data <- readr::read_csv(file = "data/2017.csv")
data$Happiness.Score <- as.integer(data$Happiness.Score)

```

## 1_Plot: Happiness Score and GDP per Capital
```{r}
library (ggplot2)
g <- ggplot(data = data, 
mapping = aes(x = Economy..GDP.per.Capita. , y = Happiness.Score, color = Health..Life.Expectancy.)
)
g <- g + geom_smooth()
g <- g + geom_point()
g
```

## 2_Ranking: Contries and their Scores
```{r}
library(plotly)
p <- ggplot(data = data, aes(x = Happiness.Score, y = reorder(Country, Happiness.Score))) + geom_point(colour = "red", alpha = .5) + geom_segment(aes(yend=reorder(Country, Happiness.Score)), xend = 0, colour="pink", alpha = .5) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + 
labs(title = "World Happiness Rank in 2017", y = "Country", x = "Happiness.Score")
usethis::use_package("plotly")
ggplotly(p)
```

```{r}

```
